---
title: "Example of a Simulation Study using Randomly Generated IRT Data"
author: "Nina van Gerwen (1860852)"
date: "21-01-2023"
output: html_document
---

## Loading the functions

To load the functions, we use source() and choose the appropriate files. To 
find out how the functions work exactly, please look at the function files directly.

```{r IRF calculation functions}
## Data generation is based on three models, therefore we created functions for
## the calculations of every model (1PL - 2PL - 3PL)

source("Functions/model-calculations.R")
source("Functions/data-generation.R")
source("Functions/missingness.R")
source("Functions/fit-indices calculations.R")
source("Functions/data-aggregation.R")

```


## Generating IRT data

With these functions, we can now generate Item Response Theory (IRT) data in the following way:

```{r}
## First set a seed for reproducibility
set.seed(1248)

## And then make use of the data.gen function with a specified 
## sample size, test length and model type to base the calculations on
test_data <- data.gen(n = 1500, k = 5, model = "2PL")
```

In case we are interested in missing data, we can also make a percentage
of our data missing by doing the following:

```{r}
## Again, set a seed for reproducibility
set.seed(1248)

## And use the missify() function, with the first argument the dataset
## and the second argument the percentage of missing data you would like
missing_test_data <- missify(test_data, .20)
```


## Using generated IRT data in a simulation study

Now, let us use these functions in a simulation study. More specifically,
we will be evaluating the performance of two fit indices, the Tucker-Lewis Index and
Comparative Fit Index, in the IRT framework.

```{r}
## LTM to fit the required models
require(ltm)
## DPLYR for some tidying
require(dplyr)
## MAGRITTR for the pipe
require(magrittr)

## Here, you can define the levels of the factors you want to investigate
## for the simulation study,
test_length <- as.factor(c(5, 10, 20))
sample_size <- as.factor(c(200, 300, 500, 1000, 1500))

## And you set the number of replications you want
n_sim <- 300

## Our output will be a data frame with first the conditions, and then the
## results, and we pre-define the data frame here with some NAs
null_results <- data.frame(test_length = NA, sample_size = NA, TLI_M = NA,
                          TLI_SE = NA, CFI_M = NA, CFI_SE = NA)

## Then set a seed for reproducibility
set.seed(1248)

## And now we start a nested for loop for the study

## With first a for loop for both factors
for(a in levels(test_length)){

  for(b in levels(sample_size)){
      
      ## Then, in every condition, you create an empty vector of size
      ## equal to the number of replications for the fit indices
      tli_values <- rep(NA, n_sim)
      cfi_values <- rep(NA, n_sim)
      
      ## You get the correct level of the factors as numerics
      temp_n <- as.numeric(as.character(b))
      temp_k <- as.numeric(as.character(a))
      
        ## And then you get results for every condition by for every
        ## replication, doing the following:
        for(j in 1:n_sim){
    
          ## Generating data according to the factors
          temp_data <- data.gen(n = temp_n, k = temp_k, model = "2PL")
                        
          ## Fitting the hypothesized model
          l_0 <- ltm(temp_data ~ z1, IRT.param = TRUE)$log.Lik
          
          ## Aggregrating the data
          aggr_data <- score.pattern.aggr(temp_data, temp_n)
          
          ## And then calculating the TLI and CFI values through our
          ## specialized functions
          tli_values[j] <- TLI(l_0, temp_data, aggr_data, temp_n, temp_k)
          
          cfi_values[j] <- CFI(l_0, temp_data, aggr_data, temp_n, temp_k)
          
        }
      
      ## Then, after the values have been calculated n_sim times, 
      ## we can get their mean and standard deviation and add these
      ## to the result dataframe through rbind()
      null_results <- rbind(null_results, c(a, b, mean(tli_values), sd(tli_values),
                                          mean(cfi_values), sd(cfi_values)))

  }
  
}

## Now we just have to clean up the dataframe by removing the first row
null_results <- null_results[-1 ,]
## And resetting the rownames
rownames(null_results) <- NULL

## And tada! your results for the 'null-condition'
null_results
```

These results show what values the TLI has on average when the hypothesized
model is also the true model. 

```{r}
## For reproducibility, we include the sessionInfo
sessionInfo()
```

